\LARGE \bf Steering a Swarm Using Global Inputs And Swarm Statistics

### 2016-08-08 journalSwarmControl/SwarmControlIJRR.tex
Added Policy Iteration Algorithm
updated MDP and policy iteration, did all captions, added new pic, removed extra images

\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\homog}{homog}
\DeclareMathOperator{\domain}{dom}
\DeclareMathOperator{\range}{range}
\DeclareMathOperator{\sign}{sgn} 
\DeclareMathOperator{\argmax}{arg\,max}
\DeclareMathOperator{\area}{area}
\DeclareMathOperator{\atan2}{atan2}

@@

%\author{Shiva Shahrokhi, Chris Ertel, Mable Wan,Lillian Lin}
%\author{Aaron~T.~Becker}
%\affil[1]{Dept.\ Electrical \& Computer Engineering, University of Houston\thanks{ University of Houston, Houston, TX, 77004 USA {\tt\small sshahrokhi2@uh.edu}}
%}
%\affil[2]{Independent}
\author{Shiva Shahrokhi, Chris Ertel, Mable Wan, Lillian Lin, Aaron T. Becker\thanks{Authors are with the Department of Electrical and Computer Engineering, University of Houston, Houston, TX, 77004 USA {\tt\small sshahrokhi2@uh.edu,atbecker@uh.edu}}
 %end thanks
} % end author block 
\maketitle
\begin{abstract}
Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion. We want to use large swarms of robots to perform manipulation tasks; unfortunately, human-swarm interaction studies as conducted today are limited in sample size, are difficult to reproduce, and are prone to hardware failures. We present an alternative.

>>>>

\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\cone}{cone}
\DeclareMathOperator{\homog}{homog}
\DeclareMathOperator{\domain}{dom}
\DeclareMathOperator{\range}{range}
\DeclareMathOperator{\sign}{sgn} 
\DeclareMathOperator{\argmax}{arg\,max}
\DeclareMathOperator{\area}{area}
\DeclareMathOperator{\atan2}{atan2}
\DeclareMathOperator*{\argmax2}{argmax}

@@

%\author{Shiva Shahrokhi, Chris Ertel, Mable Wan,Lillian Lin}
%\author{Aaron~T.~Becker}
%\affil[1]{Dept.\ Electrical \& Computer Engineering, University of Houston\thanks{ University of Houston, Houston, TX, 77004 USA {\tt\small sshahrokhi2@uh.edu}}
%}
%\affil[2]{Independent}
\author{Shiva Shahrokhi, Chris Ertel, Mable Wan, Lillian Lin, Aaron T. Becker\thanks{Authors are with the Department of Electrical and Computer Engineering, University of Houston, Houston, TX, 77004 USA, {\tt\small sshahrokhi2@uh.edu,atbecker@uh.edu}}
 %end thanks
} % end author block 
\maketitle
\begin{abstract}
Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion. We want to use large swarms of robots to perform manipulation tasks; unfortunately, human-swarm interaction studies as conducted today are limited in sample size, are difficult to reproduce, and are prone to hardware failures. We present an alternative.

### 2016-08-08 journalSwarmControl/conclusion.tex
updated MDP and policy iteration, did all captions, added new pic, removed extra images

This paper first examines the perils, pitfalls, and possibilities we discovered by launching \href{http://www.swarmcontrol.net}{SwarmControl.net}, an online game where players steer swarms of up to 500 robots to complete manipulation challenges. We record statistics from thousands of players, and use the game to explore aspects of large-population robot control. We present the game framework as a new, open-source tool for large-scale user experiments. One surprising result was that humans completed an object manipulation task \emph{faster} when provided with only the mean and variance of the robot swarm than with full-state feedback. Inspired by human operators, this paper next investigates controllers that use only the mean and variance of a robot swarm. We prove that the mean position is controllable, then provide conditions under which variance is controllable.  We next derive automatic controllers for these and a hybrid, hysteresis-based switching control to regulate the first two moments of the robot distribution.  Finally, we employ these controllers as primitives for an object manipulation task and implement all the automatic controllers on 100 kilobots controlled by the direction of a global light source.

There are many avenues for future work.  Manipulation by large populations of robots is an immature area and there are many open questions. We invite other collaborators to submit their own experiments to SwarmControl.net.
Topics of interest include control with nonuniform flow such as fluid in an artery, gradient control fields like that of an MRI, competitive playing, multi-modal control, and targeted drug delivery in a vascular network.

>>>>

This paper first examines the perils, pitfalls, and possibilities we discovered by launching \href{http://www.swarmcontrol.net}{SwarmControl.net}, an online game where players steer swarms of up to 500 robots to complete manipulation challenges. We record statistics from thousands of players, and use the game to explore aspects of large-population robot control. We present the game framework as a new, open-source tool for large-scale user experiments. One intriguing result was that humans completed an object manipulation task \emph{faster} when provided with only the mean and variance of the robot swarm than with full-state feedback. Inspired by human operators, this paper next investigates controllers that use only the mean and variance of a robot swarm. We prove that the mean position is controllable, then provide conditions under which variance is controllable.  We next derive automatic controllers for these and a hybrid, hysteresis-based switching control to regulate the first two moments of the robot distribution.  Finally, we employ these controllers as primitives for an object manipulation task and implement all the automatic controllers on 100 kilobots controlled by the direction of a global light source.

There are many avenues for future work.  Manipulation by large populations of robots has many open questions. We invite other collaborators to submit their own experiments to SwarmControl.net.
Topics of interest include control with nonuniform flow such as fluid in an artery, gradient control fields like that of an MRI, competitive playing, multi-modal control, and targeted drug delivery in a vascular network.

### 2016-08-08 journalSwarmControl/expResults.tex
Newer version
updated MDP and policy iteration, did all captions, added new pic, removed extra images

We designed five experiments to investigate human control of large robotic swarms for manipulation tasks.  Screenshots of each experiment are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of robots for manipulation, four levels of visual feedback, three control architectures, different levels of Brownian noise, and position control with 1 to 10 robots. The users could choose which experiment to try, and then our architecture randomly assigned a particular parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

\begin{figure}
\begin{overpic}[width = 0.48\columnwidth]{gamesPerPlayer.pdf}\end{overpic}
\begin{overpic}[width = 0.48\columnwidth]{measureLearning.pdf}\end{overpic}
\caption{
\label{fig:Learning}
(Left) The total number of games played per player drops off exponentially. (Right) We are able to show that players skill improves as they retry tests using data from \emph{Varying Number}
}
\end{figure}

% RESULTS
%% For each task, list the hypothesis, then give plot

%\begin{figure}
%\centering
%\begin{overpic}[width = 0.5\columnwidth]{DesignSpace.pdf}\end{overpic}
%\caption{
%\label{fig:DesignSpace} 
%There is a multi-dimensional design space for controlling robot swarms.  In this paper we provide a framework for exploring this design space. To demonstrate the capabilities of this framework, in Section \ref{sec:experiments} we describe experiments that test task completion time as a function of the number of robots, the quality of the state feedback, and the control architecture.}
%\end{figure}

\paragraph{Varying number}
\begin{figure}
\centering
\begin{overpic}[width = 0.5\columnwidth]{ResVaryNum.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:ResVaryNu}Data from \emph{Varying Number} using robots to push an object through a maze to a goal location.  The data indicates that this task has an optimal number of robots, perhaps due to the relative sizes of the robots, obstacles, and object. Best-fit linear and quadratic lines are overlaid for comparison. 
%\vspace{-1em}
}
\end{figure}

@@

The results were conclusive, as shown in Fig.~\ref{fig:ResVaryControlVis}.a: attractive control was the fastest, followed by global control, with repulsive control a distant last.  The median time using repulsive control was four times longer than with attractive control.

@@

\begin{figure}[b!]
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{ResVaryControl.pdf}\end{overpic}
\begin{overpic}[width =\figwid]{ResVaryVis.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:ResVaryControlVis} Left: Attractive control resulted in the shortest completion time and repulsive the longest for building a three-block pyramid. Right: Completion-time results for the four levels of visual feedback shown in Fig.~\ref{fig:Visualization}. Surprisingly, players perform better with limited feedback--subjects with only the mean + variance  outperformed all others.
%\vspace{-1em}
}
\end{figure}

@@

To our surprise, our experiment indicates the opposite: players  with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryControlVis}.b shows, the levels of feedback arranged by increasing completion time are [mean + variance, mean, full-state, convex-hull].  Anecdotal evidence from beta-testers who played the game suggests that tracking 100 robots is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers found convex-hull feedback confusing and irritating.  A single robot left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

@@

\paragraph{Position control}
This online experiment examined how completion time scales with the number of robots $n$. Using a single square obstacle, users arranged $n\in[1,10]$ robots into a specified goal pattern.  The goal pattern formed a block `A' with 10 robots, and lesser numbers of robots used a subset of these goal positions. Our hypothesis was that completion time would increase linearly with the number of robots, as with our position control algorithm in \cite{Becker2013b}.  Our results roughly corroborate this, as shown in Fig.~\ref{fig:ResVaryNoisePosition}.b.  Though the number of robots presented to game players is uniformly distributed, larger $n$ are more difficult, and the number of successful experiments drops steadily as $n$ increases.

>>>>

We designed five experiments to investigate human control of large robotic swarms for manipulation tasks.  Screenshots of each experiment are shown in Fig.~\ref{fig:5experiments}.  Each experiment examined the effects of varying a single parameter: population of robots for manipulation, four levels of visual feedback, three control architectures, different levels of Brownian noise, and position control with 1 to 10 robots. The users could choose which experiment to try, and then our architecture randomly assigned a particular parameter value for each trial.  We recorded the completion time and the participant ID for each successful trial.  
%As Fig.~\ref{fig:Learning} shows, one-third of all participants played only a single game.  Still, many played multiple games, and their decreasing completion times demonstrates their skills improved.

\paragraph{Varying number}
\begin{figure}
\begin{overpic}[width = 0.5\columnwidth]{ResVaryNum.pdf}\end{overpic}
\begin{overpic}[width = 0.48\columnwidth]{measureLearning.pdf}\end{overpic}
\caption{
\label{fig:ResVaryNu}Data from \emph{Varying Number} using robots to push an object through a maze to a goal location.  (Left) Data indicates this task has an optimal number of robots, perhaps due to the relative sizes of the robots, obstacles, and object. Best-fit linear and quadratic lines are overlaid for comparison. 
(Right) Skill improves as players retry tests using data from \emph{Varying Number}.
}
\end{figure}

@@

The results were conclusive, as shown in Fig.~\ref{fig:ResVaryControlVis}.a: attractive control was the fastest, followed by global control, with repulsive control a distant last.  The median time using repulsive control was four times longer than with attractive control.
Using ANOVA analysis, we reject the null hypothesis that all controllers are equivalent, with $p$-value $3.37\times10^{-32}$.

@@

\begin{figure}[b!]
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{ResVaryControl.pdf}\end{overpic}
\begin{overpic}[width =\figwid]{ResVaryVis.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:ResVaryControlVis} Left: Attractive control resulted in the shortest completion time and repulsive the longest for building a three-block pyramid. Right: Completion-time results for the four levels of visual feedback shown in Fig.~\ref{fig:Visualization}.  Players performed better with limited feedback.
%\vspace{-1em}
}
\end{figure}

@@

Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryControlVis}.b shows, the levels of feedback arranged by increasing completion time are [mean + variance, mean, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing
Using ANOVA analysis, we reject the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 robots is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers found convex-hull feedback confusing and irritating.  A single robot left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

@@

\paragraph{Position control}
This online experiment examined how completion time scales with the number of robots $n$. Using a single square obstacle, users arranged $n\in[1,10]$ robots into a specified goal pattern.  The goal pattern formed a block  {\sffamily A} with 10 robots, and lesser numbers of robots used a subset of these goal positions. Our hypothesis was that completion time would increase linearly with the number of robots, as with our position control algorithm in \cite{Becker2013b}.  Our results roughly corroborate this, as shown in Fig.~\ref{fig:ResVaryNoisePosition}.b.  Though the number of robots presented to game players is uniformly distributed, larger $n$ are more difficult, and the number of successful experiments drops steadily as $n$ increases.

### 2016-08-08 journalSwarmControl/experiment.tex
updated MDP and policy iteration, did all captions, added new pic, removed extra images

This section analyzes an \emph{object manipulation} task attempted by both our hybrid, hysteresis-based controller and by human users.

\subsection{Human-controlled object manipulation}

As reported in the previous section, players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryControlVis}.b shows, the levels of feedback arranged by increasing completion time are [mean, mean + variance, full-state, convex-hull].  Interviews with  beta-testers suggests that tracking 100 robots was overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance was like using a ``spongy'' manipulator. Convex-hull feedback was confusing and irritating because a single robot left behind an obstacle would distort the entire hull, obscuring the information about the majority of the swarm.
%obscuring what the rest of the swarm is doing.

\subsection{Learning a policy for the object}
The swarm must deliver the object to the goal region.  To solve this object manipulation task, we first discretize the environment.

In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid to determine $\mathbf{M}_{BFS}$, the shortest distance from any grid cell to the goal, and generated a gradient map $\nabla \mathbf{M}$ toward the goal as shown in Fig.~\ref{fig:BFSGradient}.  The object's center of mass is at $\mathbf{b}$ and has average radius $r_b$. 
The robots were directed to assemble behind the object at  $\mathbf{b} - k_2 r_b \nabla \mathbf{M}(\mathbf{b})$, then move to  $\mathbf{b} - k_3 r_b \nabla \mathbf{M}(\mathbf{b})$ to push the object toward the goal location. However, BFS has no penalties on object collisions with obstacles, and the resulting collisions made the BFS solution slow.

\todo{PI stuff: shiva does this} Policy iteration to learn $\mathbf{M}_{MDP}$, for a book chapter on PI, see \cite{Thrun2005}.  All grid locations at the goal were assigned a large reward, each grid location was assigned a small cost, and grid locations next to obstacles were assigned a high cost.
Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal, cite book.

$\mathbf{M}_{BFS}$, and $\mathbf{M}_{MDP}$ are shown in Fig.~\ref{fig:BFSGradient}.
\todo{report results of 10 simulations with BFS and with PI.  Give mean and std}

\begin{figure}
\centering
\begin{overpic}[scale=0.19]{GradientView.png}
\end{overpic}
\begin{overpic}[scale=0.19]{PolicyIter.png}
\end{overpic}
\begin{overpic}[scale=0.262]{MDPmap.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:BFSGradient}The BFS algorithm finds the shortest path for the moveable object  to compute gradient vectors (left). Using policy iterations enables encoding penalties for being near obstacles (middle). At right, the results of policy iteration on our experimental setup.
%\vspace{-2em}
}
\end{figure}

@@

\todo{report results of 10 simulations with and without Potential fields.  Give mean and std}
\begin{figure}
\centering
\begin{overpic}[width=1\columnwidth]{PotentialField.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:potentialField} The attractive filed source is centered on (left). Repulsive field source is centered at object's COM (middle). We use a combined forces to use this method to avoid pushing the object backwards (right).}
\end{figure}

@@

\begin{figure*}
\begin{center}
	\begin{overpic}[width=0.45\columnwidth]{mainRegions.pdf}\end{overpic}
	\begin{overpic}[width=0.45\columnwidth]{transferRegions.pdf}\end{overpic}\\
	\vspace{0.5em}
	\begin{overpic}[width=0.6\columnwidth]{stateMachine.pdf}\end{overpic}
\end{center}
\caption{\label{fig:Region} The state machine and regions.
}
\end{figure*}

@@

\begin{algorithm}
\caption{Object-manipulation controller for a robotic swarm.}\label{alg:BlockPushing}
\begin{algorithmic}[1]
\Require Knowledge of moveable object's center of mass $\mathbf{b}$; swarm mean $[\bar{x},\bar{y}]$ and variance $[\sigma_x^2, \sigma_y^2]$, each calculated using the regions function from \S \ref{subsec:OutlierRejection};  map of the environment
\State Compute $\mathbf{M}$, the cost to goal    \Comment{using $\mathbf{M}_{BFS}$ or $\mathbf{M}_{MDP}$} 
\State Compute the gradient, $\nabla \mathbf{M}$
\While{$\mathbf{b}$ is not in goal region}
\State $\sigma^2 \gets \max{(\sigma_x,\sigma_y)}$
\If {$\sigma^2 > \sigma_{max}^2$}
\While{$\sigma^2 > \sigma_{min}^2$}
\State $ [x_{goal}, y_{goal}] \gets $ the nearest corner in current region
\State Apply \eqref{eq:PDcontrolPosition} to move toward $[x_{goal}, y_{goal}]$
\EndWhile
\Else  
%\If {$\mathrm{distance}( \mathbf{b}, [x_{goal}, y_{goal}] ) > k_1 r_b$}
%	\State$r_p \gets k_2 r_b$  \Comment{guarded move}
%	\Else
%	\State$r_p \gets k_3 r_b$  \Comment{pushing move}
%	\EndIf
%\State$r_p \gets k_3 r_b$  \Comment{pushing move}
\State Apply \eqref{eq:potentialfield}   \Comment{potential field to push object in correct direction}
\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

The interaction between the robots and object is impulsive so, like the study of impulsive pulling in  \cite{christensen2016let},  adding additional robots decreases completion time, but with diminishing returns.  After 75 robots, additional robots no longer can interact with the object and do not contribute to the task success.

Brownian noise adds stochasticity.  This randomness can break the object free if it is stuck, but diminishes the effect of the control input.  Large amounts of noise increase completion time.

The robots have limited force, so increasing the object weight increases completion time.

\begin{figure*}
\centering
%\renewcommand{\figwid}{0.19\columnwidth}
%\href{http://youtu.be/tCej-9e6-4o}{\begin{overpic}[width =\figwid]{story1.png}\put(6,15){T = 5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story2.png}\put(6,15){T = 12 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story3.png}\put(6,15){T = 20 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story4.png}\put(6,15){T = 25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story5.png}\put(6,15){T = 33 s}
%\end{overpic}}
\begin{overpic}[width =\columnwidth]{SwarmRun.pdf}
\end{overpic}
\vspace{-1em}
\caption{\label{fig:story}\href{http://youtu.be/tCej-9e6-4o}{Snapshots showing an object manipulation simulation with 100 robots under automatic control.  See animation in~\cite{ShivaVideo2015}.}
%\vspace{-2em}
}
\end{figure*}

>>>>

This section analyzes an \emph{object manipulation} task attempted by both our hybrid, hysteresis-based controller, inspired by the analysis of human users in Section~\ref{sec:expResults}.  
The swarm must deliver the object to the goal region.  To solve this object manipulation task, we divide the task into two components: designing a policy for the object, and designing a control law for the swarm to push the object according to the policy.

\subsection{Learning a policy for the object}\label{subsec:objectpolicy}

To design the policy, we first discretize the environment. 
In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid to determine $\mathbf{M}_{BFS}$, the shortest distance from any grid cell to the goal, and generated a gradient map $\nabla \mathbf{M}$ toward the goal as shown in Fig.~\ref{fig:BFSGradient}.  
The object's center of mass is at $\mathbf{b}$ and has average radius $r_b$. 
The robots were directed behind the object at  $\mathbf{b} - 1.5 r_b \nabla \mathbf{M}(\mathbf{b})$, then directed to  $\mathbf{b} - 0.1 r_b \nabla \mathbf{M}(\mathbf{b})$ to push the object toward the goal location. However, BFS has no penalties on object collisions with obstacles, and the resulting collisions made the BFS solution slow.

 To avoid obstacles, this paper models object movement as a Markov Decision Process (MDP) with non-deterministic movement.  
  Value iteration,  as described in \cite{Thrun2005}, is used to learn an \emph{optimal policy}: a function that assigns a control input to every possible state.
 At each state the object can be commanded to move in one of eight directions with a small probability of moving in the wrong direction.

 A corresponding reward function gives a high reward to the goal state,  
 a large negative reward to states including obstacles, and a small negative reward to all other states.
The reward function $r(x,u)$ is defined as
\begin{align}
r(x,u) &=  \left\{
\begin{array}{ll}
     +100, &  \textrm{if } u \textrm{ leads to goal state}\\
      -100, & \textrm{if } u \textrm{ leads to a state with an obstacle} \\
      -1, & \textrm{otherwise}\\
\end{array} 
\right.
\end{align}
where $u$ is the action and $x$ is the current state. 
  Value iteration iteratively learns the value $\hat{V}(x)$ for the object being in each state $x$. The optimal policy is the control action that, in probability, results in the largest value:
   \begin{align} \arg\max_u   [ r(x,u) + \sum\limits_{j=1}^N \hat{V}(x_j) p(x_j| u,x)].  \label{eq:OptimalPolicy}
   \end{align}
   The value function $\hat{V}(x_j) $ is calculated by computing the value $\hat{V}$ for all $N$ states and iterating until convergence:
\begin{align}
\text{for }&\text{$i=1$ to $N$ do} \nonumber \\
&\hat{V} (x_j) = \gamma \max_u [r(x_j,u) + \sum\limits_{i=1}^N \hat{V}(x_i) p(x_i| u,x_j)] \label{eq:ValueIteration}\\
\text{end}& \nonumber
\end{align}
In our experiments $\gamma = 0.97$, and \eqref{eq:ValueIteration} was iterated 200 times. A {\sc Matlab} implementation of this algorithm is available at \todo{link to algorithm}.  
%Rather than a shortest distance to goal, $\nabla \mathbf{M}_{MDP}$  gives the approximate minimum cost to goal.

$\mathbf{M}_{BFS}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 robots, pushing the object to goal using $\mathbf{M}_{BFS}$ required $\mu=XX, \sigma=YY$s while  $\mathbf{M}_{MDP}$ required $\mu=XX, \sigma=YY$.
\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

\begin{figure}
\centering
\begin{overpic}[scale=0.19]{GradientView.png}
\end{overpic}
\begin{overpic}[scale=0.19]{PolicyIter.png}
\end{overpic}
\begin{overpic}[scale=0.262]{MDPmap.pdf}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:BFSGradient}The BFS algorithm finds the shortest path for the moveable object  to compute gradient vectors (left). Modeling as an MDP enables encoding penalties for being near obstacles. (Middle) The control policy from value iteration. (Right) Value function and control policy for the hardware setup. The vision algorithm detects obstacles.
%\vspace{-2em}
}
\end{figure}

@@

In 10 simulations with 100 robots, pushing the object to goal without a repulsive potential field failed in xx of YY runs. No failures occurred with the  repulsive potential field.  Of successful trials, completion time without repulsive potential fields required $\mu=XX, \sigma=YY$s while using repulsive potential fields required $\mu=XX, \sigma=YY$.
\todo{report results of 10 simulations with and without Potential fields.  Give mean and std}

\begin{figure}
\centering
\begin{overpic}[width=1\columnwidth]{PotentialField.pdf}\end{overpic}
%\todo{I like the 'target' symbol, but it is not self-documenting.  We need a legend explaining the min and max variance ellipses, the goal region, the variance, the mean, the object COM, and the target mean position.  I think these are easiest to make in powerpoint.
%Please use the same color and line style for the variance min and max as you use in Figure 4.
%}
%{blockpushingImageWithMeanAndVarianceOverlay.png}
\caption{\label{fig:potentialField} (Left) The attractive field is centered behind the object's COM. (Middle) The repulsive field is centered at the object's COM. (Right) Combining these forces prevents the swarm from pushing the object backwards.}
\end{figure}

@@

\begin{figure*}
\begin{center}
	\begin{overpic}[width=0.45\columnwidth]{mainRegions.pdf}\end{overpic}
	\begin{overpic}[width=0.45\columnwidth]{transferRegions.pdf}\end{overpic}\\
	\vspace{0.5em}
	\begin{overpic}[width=0.6\columnwidth]{stateMachine.pdf}\end{overpic}
\end{center}
\caption{\label{fig:Region}  Outlier rejection state machine and regions.
}
\end{figure*}

@@

\begin{algorithm}
\caption{Object-manipulation controller for a robotic swarm.}\label{alg:BlockPushing}
\begin{algorithmic}[1]
\Require Knowledge of moveable object's center of mass $\mathbf{b}$; swarm mean $[\bar{x},\bar{y}]$ and variance $[\sigma_x^2, \sigma_y^2]$, each calculated using the regions function from \S \ref{subsec:OutlierRejection};  map of the environment
\State Compute optimal policy for object, according to \S \ref{subsec:objectpolicy}
\While{$\mathbf{b}$ is not in goal region}
\State $\sigma^2 \gets \max{(\sigma_x,\sigma_y)}$
\If {$\sigma^2 > \sigma_{max}^2$}
\While{$\sigma^2 > \sigma_{min}^2$}
\State $ [x_{goal}, y_{goal}] \gets $ the nearest corner in current region
\State Apply \eqref{eq:PDcontrolPosition} to move toward $[x_{goal}, y_{goal}]$
\EndWhile
\Else  
%\If {$\mathrm{distance}( \mathbf{b}, [x_{goal}, y_{goal}] ) > k_1 r_b$}
%	\State$r_p \gets k_2 r_b$  \Comment{guarded move}
%	\Else
%	\State$r_p \gets k_3 r_b$  \Comment{pushing move}
%	\EndIf
%\State$r_p \gets k_3 r_b$  \Comment{pushing move}
\State Calculate $\nabla \mathbf{M}(\mathbf{b})$  \Comment{policy for object at $\mathbf{b}$}
\State Apply \eqref{eq:potentialfield}   \Comment{potential field to push object in correct direction}
\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\begin{figure*}
\centering
%\renewcommand{\figwid}{0.19\columnwidth}
%\href{http://youtu.be/tCej-9e6-4o}{\begin{overpic}[width =\figwid]{story1.png}\put(6,15){T = 5 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story2.png}\put(6,15){T = 12 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story3.png}\put(6,15){T = 20 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story4.png}\put(6,15){T = 25 s}
%\end{overpic}
%\begin{overpic}[width =\figwid]{story5.png}\put(6,15){T = 33 s}
%\end{overpic}}
\begin{overpic}[width =\columnwidth]{SwarmRun.pdf}
\end{overpic}
\vspace{-2em}
\caption{\label{fig:story}\href{http://youtu.be/tCej-9e6-4o}{Snapshots showing an object manipulation simulation with 100 robots under automatic control.  See animation in~\cite{ShivaVideo2015}.}
%\vspace{-2em}
}
\end{figure*}

The interaction between the robots and object is impulsive so, like the study of impulsive pulling in  \cite{christensen2016let},  adding additional robots decreases completion time, but with diminishing returns. 
 After 75 robots, additional robots no longer can interact with the object and do not contribute to the task success. 
Brownian noise adds stochasticity.  This randomness can break the object free if it is stuck, but diminishes the effect of the control input.  Large amounts of noise increase completion time.
The robots have limited force, so increasing the object weight increases completion time.  
 Rectangles and squares tend to get stuck in the 90$^\circ$ workspace corners, and cause longer completion times than circles and hexagons.

### 2016-08-08 journalSwarmControl/realExperiment.tex
updated MDP and policy iteration, did all captions, added new pic, removed extra images

\begin{figure*}
\begin{center}
	\begin{overpic}[width=\columnwidth]{RealMean}\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\caption{\label{fig:realMean}
Mean control plot with kilobots. %\todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red crcle in left hand corner of these, and put a scale bar in image}
}
\end{figure*}

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=.9\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(49,8){\emph{t} = 2185 s}\put(83,8){\emph{t} = 2703 s}
\end{overpic}
\vspace{-1em}
\caption{\label{fig:expSnapShot}{Snapshots showing the object manipulation experiment with 100 kilobots under automatic control. The automatic controller will see the pink objects as obstacles and finds its path to the goal. See the video attachment for an animation~\cite{ShivaVideo2015}}
%\vspace{-2em}
}
\end{figure}

>>>>

\begin{figure*}
\begin{center}
	\begin{overpic}[width=\columnwidth]{RealMean}\end{overpic}
%	\begin{overpic}[width=0.35\columnwidth]{XYMeanControl.eps}\end{overpic}
\end{center}
\vspace{-1em}
\caption{\label{fig:realMean}
Regulating average $x$ position of 100 kilobots using control law \eqref{eq:PDcontrolPosition}.
%Mean control plot with kilobots. %\todo{place a red star and a red circle at two spots on graph, put two images of the swar at right with a red star and red circle in left hand corner of these, and put a scale bar in image}
}
\end{figure*}

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=.9\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(49,8){\emph{t} = 2185 s}\put(83,8){\emph{t} = 2703 s}
\end{overpic}
\vspace{-1em}
\caption{\label{fig:expSnapShot}{Snapshots showing the object manipulation experiment with 100 kilobots under automatic control. The automatic controller classifies pink objects as obstacles and generates a policy to the goal. See the video attachment for an animation~\cite{ShivaVideo2015}}
%\vspace{-2em}
}
\end{figure}
